%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{casual}                             % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{\huge{Rashmi}}{\huge{Mudduluru}}
\title{\large{\\ email: rashmi.m.cit@gmail.com \\ website: \href{https://sites.google.com/view/rashmi}{https://sites.google.com/view/rashmi} \\ PhD Applicant, Computer Science Department}}
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle

\vspace{-10pt}

\section{Research Interests}
\cvitem{}{My research interests lie broadly in the areas of Programming Languages, Verification,
and Software Engineering.}

\section{Education}
\cventry{2012--2015}{M.Sc(Engg), Computer Science}{Indian Institute of Science}{Bangalore}
{}{CGPA: 6.3/8, Advisor: Dr. Murali Krishna Ramanathan \newline{} Thesis: Efficient Instrumentation for Object Flow Profiling}  % arguments 3 to 6 can be left empty
\cventry{2006--2010}{B.E, Computer Science}{Coimbatore Institute of Technology}{Coimbatore}{}{CGPA - 9.24/10}

\section{Work Experience}
\cventry{2015--present}{Research Fellow}{Microsoft Research, India}{Bangalore}{}{Mentor: Dr. Akash Lal}
\cventry{2010--2012}{Software Engineer}{Aricent Technologies}{Bangalore}{}{}

\section{Conference Publications}
\cvitem{ISSTA 2016}{Rashmi Mudduluru, Murali Krishna Ramanathan, \textbf{Efficient Flow Profiling for Detecting Performance Bugs}, 25th International Symposium on Software Testing and Analysis, 2016.}
\cvitem{FAST 2016}{Pantazis Deligiannis, Matt McCutchen, Paul Thomson, Shuo Chen, Alastair F. Donaldson, 
John Erickson, Cheng Huang, Akash Lal, Rashmi Mudduluru, Shaz Qadeer, Wolfram Schulte,  \textbf{Uncovering Bugs in Distributed Storage Systems during Testing (Not in Production!)}, 14th USENIX Conference on File and Storage Technologies, 2016.}
\cvitem{ISSTA 2015}{Monika Dhok, Rashmi Mudduluru, Murali Krishna Ramanathan, \textbf{Pegasus: Automatic Barrier Inference for Stable
Multithreaded Systems}, 2015 International Symposium on Software Testing and Analysis.}
\cvitem{FASE 2014}{Rashmi Mudduluru, Murali Krishna Ramanathan, \textbf{Efficient Incremental Static Analysis Using Path Abstraction}, 17th International Conference on Fundamental Approaches to Software Engineering, 2014.}

\section{Selected Projects}
\cvlistitem{Implemented a dynamic data race detector for programs written in P\#, a DSL for asynchronous programs. Dynamic instrumentation was done with the help of Extended Reflection, a library that facilitates inserting callbacks for MSIL instructions.}
\cvlistitem{Designed and built a profiler that tracks the precise data path taken by objects in Java programs. Implementation was done in Java on top of Calfuzzer/Soot framework.}
\cvlistitem{Built an incremental static analyzer on top of SATURN, a constraint based
static analysis tool for finding bugs. Implementation was done in OCaml and Berkeley DB.}
\cvlistitem{Implemented a static null pointer dereference analysis tool for Java programs using the
Soot bytecode analysis framework.}

\section{Graduate Courses}
\cvitem{}{Program analysis and verification, Design and analysis of algorithms, Automata theory and
computability, Topics in software bug detection, Automated verification.}


\section{Service}
\cvlistitem{Teaching Assistant for the graduate course \textit{Automata Theory and Computability.}}
\cvlistitem{Student volunteer at \textit{International Conference on Software Engineering (ICSE) 2014.}}

\section{Awards and Scholarships}
\cvlistitem{ACM SIGSOFT Distinguished paper award for the paper \textit{Efficient Flow Profiling for Detecting Performance Bugs} at ISSTA 2016.}
\cvlistitem{Received the PLMW scholarship for attending POPL 2015.}
\cvlistitem{Secured 99.7 percentile in Graduate Aptitude Test in Engineering (GATE) 2012.}

\section{References}
\cvitem{}{Dr. Akash Lal \newline{} Senior Researcher, \newline{} Microsoft Research, India,
\newline{} \href{https://www.microsoft.com/en-us/research/people/akashl/}{https://www.microsoft.com/en-us/research/people/akashl/}\newline{}}

\cvitem{}{Dr. Murali Krishna Ramanathan \newline{} Assistant Professor, Department of Computer Science and 
Automation, \newline{} Indian Institute of Science,
\newline{} \href{http://drona.csa.iisc.ac.in/~muralikrishna/}{http://drona.csa.iisc.ac.in/\textasciitilde muralikrishna/}\newline{}}

\cvitem{}{Dr. Deepak D'Souza \newline{} Associate Professor, Department of Computer Science and 
Automation, \newline{} Indian Institute of Science,
\newline{} \href{http://drona.csa.iisc.ernet.in/~deepakd/}{http://drona.csa.iisc.ernet.in/\textasciitilde deepakd/}}

\end{document}